---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# pokerstoveR

An R wrapper around the `ps-eval` executable from pokerstove.

## Installation

This package is not on CRAN. You can however install the development version
with `install_github`.

```{r, eval = FALSE}
devtools::install_github("GregorDeCillia/pokerstoveR")
```

In order to use the package, `pokerstove` has to be installed and `ps-eval` has to
be in the `PATH`.

## Preflop equities

Currently, there is just one useful command in the package which is called
`ps_eval`. This command relies on `ps-eval` to calculate equities of NLHE hands.

```{r example}
library(pokerstoveR)
ps_eval("AcAs", "2h7d")
```

```{r, include = FALSE}
res <- ps_eval("AcAs", "2h7d")
```


In this case we see the preflop equities of the hands `AcAs` (ace of clubs, ace of 
spades) versus `2h7d` (two of hearts, seven of diamonds). The aces 
have `r res$equity[1]`% equity.

The command `ps_eval` can be called with an arbitrarty number of hands.
However, the number of hands has to be at least two.

```{r cars}
ps_eval("AcAs", "2h7d", "KsKd", "7h8h")
```

## Postflop equities

To calculate the postflop equities, a board has to be specified using the `board` 
parameter of `ps_eval`.

```{r}
ps_eval("AcAs", "2h7d", board = "2c2d2s")
```
